Analysis

### 2022-05-30 FIMO_processing.Rmd
Make Summary a separate chunk

# Input files
fileNameIn1 <- file.path(dir_data, "")
# Output files
fileNameOut1 <- file.path(dir_data, "")
```

@@

  ctcfGR_to_save <- paste(genome_id, motif, "FIMO", sep = ".")
  fileNameOut1 <- file.path(dir_data, paste0(ctcfGR_to_save, ".RData"))
  fileNameOut1.1 <- file.path(dir_data, paste0(ctcfGR_to_save, ".bed"))
  # Assign this object to the subfolder-specific variable name
  assign(ctcfGR_to_save, ctcfGR)
  # Save as RData object. ctcfGR_to_save is the character name of the CTCF GRanges variable
  save(list = ctcfGR_to_save, file = fileNameOut1)
  # load(file = fileNameOut1)
  export.bed(eval(parse(text = ctcfGR_to_save)), fileNameOut1.1)
  # Summary
  # Width
  summary_gr <- summary(width(eval(parse(text = ctcfGR_to_save))))
  # All summary
  summary_to_save <- data.frame(File = ctcfGR_to_save,
                                N = length(width(eval(parse(text = ctcfGR_to_save)))), 
                                Min = as.numeric(summary_gr["Min."]), 
                                Median = as.numeric(summary_gr["Median"]), 
                                Mean = as.numeric(summary_gr["Mean"]), 
                                Max = as.numeric(summary_gr["Max."]))
  fileNameLog <- file.path(dir_data, "log_PWMs.csv")
  write_csv(summary_to_save, fileNameLog, append = TRUE)
}
```

@@

>>>>

# Input files
fileNameIn1 <- file.path(dir_data, "")
# Output files
fileNameOut1 <- file.path(dir_data, "log_PWMs.csv")
```

@@

  ctcfGR_to_save <- paste(genome_id, motif, "FIMO", sep = ".")
  fileNameOut1 <- file.path(dir_data, paste0(ctcfGR_to_save, ".RData"))
  fileNameOut1.1 <- file.path(dir_data, paste0(ctcfGR_to_save, ".bed"))
  # Assign this object to the subfolder-specific variable name
  assign(ctcfGR_to_save, ctcfGR)
  # Save as RData object. ctcfGR_to_save is the character name of the CTCF GRanges variable
  save(list = ctcfGR_to_save, file = fileNameOut1)
  # load(file = fileNameOut1)
  export.bed(eval(parse(text = ctcfGR_to_save)), fileNameOut1.1)
}
```

@@

# Summary

```{r}
files <- list.files(dir_data, pattern = "*.bed", full.names = TRUE)
for (file in files) {
  print(basename(file) %>% str_remove(., ".bed"))
  gr <- import.bed(file)
  # Summary
  summary_to_save <- data.frame(File = basename(file) %>% str_remove(., ".bed"),
                                Assembly = strsplit(basename(file), ".", fixed = TRUE)[[1]][1],
                                All = length(gr),
                                Reduced = length(reduce(gr)))
  write_csv(summary_to_save, fileNameOut1, append = TRUE)
}

```
